\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[green]{classic}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[portuguese]{babel}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths

\fancyfoot{} % clear all footer fields
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{\footnotesize } % other info in "inner" position of footer line

% personal data                                                                                                                                                 
\firstname{João Paulo}                                                                                                                                                
\familyname{\\ \\Madureira}
\title{Curriculum Vitae}               % optional, remove the line if not wanted                                                                                
\address{via Palazzon 7, Riese Pio X}{31039 Treviso, Italy}    % optional, remove the line if not wanted                                                        
\mobile{+39 340 5997839}                    % optional, remove the line if not wanted                                                                           
\phone{+385 92 2201317}                      % optional, remove the line if not wanted                                                                          
%\fax{312 996 1491}                          % optional, remove the line if not wanted                                                                          
\email{jpmadureira@gmail.com}                      % optional, remove the line
% if not wanted \extrainfo{additional information (optional)} % optional, remove the line if not wanted                                                                        
% \photo[84pt]{pic_enhached.jpg}          % '64pt' is the height the picture
% must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted

\begin{document}
\maketitle

\vspace{-10mm}

%Section
\section{Info}
\cvcomputer{Born}{\small October 13th, 1983 at Porto
(Portugal)\normalsize}{Citizenship}{\small Portuguese\normalsize}
\cvcomputer{Additional Address}{J.Salvadora 14, Ciglenica, 44320 Kutina, Croatia}{Driving License}{\small B\normalsize}
\cvcomputer{LinkedIn}{\small \url{http://it.linkedin.com/in/goivan}\normalsize}{Elance}{\small \url{http://ntrp.elance.com}\normalsize}
\cvcomputer{Blog}{\small \url{http://ntrpivan.blogspot.com}\normalsize}{Skype}{\small ivan.ntrp}

\vspace{-4mm}  

\section{WORK EXPERIENCE}
\vspace{-2mm}
\cventry{12/2012-Present}{Java Developer}{Blip Web
Designers}{Porto}{Portugal}{
Development and maintenance of Betfair's Sportsbook website which included:
\begin{itemize}
  \item UK and Italian websites;
  \item High performance and scalable web services supporting all of Betfair's
  sites and mobile applications.
\end{itemize}
Technologies and tools used:
\begin{itemize}
  \item Spring, Tomcat, Jetty for the website and services;
  \item Couchbase for cashing purposes;
  \item Maven, Jenkins and Chef for build and deployment management;
  \item TestNG and Selenium for integration tests.
\end{itemize}
}

\cventry{05/2011-11/2012}{Software Consultant}{Portugal Telecom
(PT)}{Lisbon}{Portugal}{
Development of an application monitoring solution for Portugal Telecom. Worked
on UI components developed with Ruby on Rails, JQuery, Sinatra and memcached,
backend message routing with Apache ActiveMQ and Camel, and MySQL for the datasource.
}

\cventry{11/2010-04/2011}{Software Developer}{Nokia Siemens Networks
(NSN)}{Aveiro}{Portugal}{
Design and implementation of a functional prototype using several new concepts
that could be added to NSN's main network and performance management solution.
This analysis not only included databases (ORACLE e PostgreSQL) but also web
components (Portlets, J2EE and GWT) and modeling tools (EMF).
}

\cventry{09/2009-10/2010}{Software Developer}{Nokia Siemens Networks
(NSN)}{Aveiro}{Portugal}{
Migration of the continuous integration process used by NSN's network and
performance management solution to a centralized (cloud based) environment.
This new environment used Bamboo for the frontend interface, Ruby on Rails for
virtual machine and artifact management, SubVersion for source control and
Maven for build management.
}

\cventry{01/2009-09/2009}{Software Developer}{Nokia Siemens Networks
(NSN)}{Aveiro}{Portugal}{
Design and implementation of a prototype for ETL handling based on ESB
(Enterprise Service BUS). The purpose of this prototype was to use Apache
ServiceMix to extracts performance metrics from network elements, process them
and load into NSN's network and performance management solution. Development of
a continuous integration process using CruiseControl for the frontend
interface, SubVersion for source control, Maven for build management and
virtualization of test machines through KVM.
}

\cventry{12/2007-12/2008}{Software Developer}{Nokia Siemens Networks
(NSN)}{Aveiro}{Portugal}{
Development of an ETL mechanism in Java to be used NSN's new network and
performance management solution. Implementation of a production pipe using Ant,
Clearcase and CruiseControl for this new solution.
}

\cventry{09/2006-11/2007}{Software Developer}{Siemens
Networks}{Aveiro}{Portugal}{
Activity developed as part of a professional trainee program.
Design and specification of a new data format used by Siemens to describe a
telecommunication network. This data format was meant to be less verbose and
error-prone. Development and test of modules for Siemens' performance
management solution in both C++ and Java.
}

\cventry{03/2006-8/2006}{Software Developer}{Siemens SA}{Perafita}{Portugal}{
Activity developed as part of a curricular trainee program.
Development of an IDE based on Eclipse RCP to aid on the development of
Siemens’s network performance management solution.
}

\section{TRAINING}

\cventry{03/2012}{}{VMWare Educational Services}{}{}{Core Spring.}
\cventry{02/2008}{}{Quality Tree Software}{}{}{Agile Testing and TDD (Test
Driven Development).}
\cventry{09/2007}{}{Learning Tree International}{}{}{Java Enterprise Application
Development - JSP, JSF, EJB3, JPA, JMS.}
\cventry{08/2007}{}{Learning Tree International}{}{}{Advanced Java Programming -
Annotations, concurrency, class loaders, NIO, JMX}

\section{EDUCATION}

\cventry{09/2005-07/2006}{CPE (Certificate of Proficiency in English)}{British
Council}{Porto}{Portugal}{
English course and ESOL exam completed with a level B (between 75\% and 79\%).
}

\cventry{09/2001-09/2006}{Licentiate in Informatics and Computing
Engineering}{Faculty of Engineering from the University of Porto
}{Porto}{Portugal}{Completed with an average of 16 out of 20.}

\end{document}
